HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-20 LaTeX/ms.tex
Cowley final comments.

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{24}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Superieure, CNRS, 24 rue Lhomond, 75005 Paris, France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  The
    ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down
    to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
    Optical or near-infrared imaging indicates that 36 of the ALMA sources
    experience a significant flux boost from gravitational lensing ($\mu >
    1.1$), but only 6 are strongly lensed and show multiple images.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov chain Monte Carlo visibility plane analysis tool to
    analyze the source properties.  Combined with our previous work on brighter
    {\it Herschel} sources, the lens models presented here tentatively favor
    intrinsic luminosity functions for DSFGs with a break near 8$\,$mJy at
    880$\,\mu$m and a steep fall off at higher flux densities.  Nearly 70\% of
    the {\it Herschel} sources break down into multiple ALMA counterparts,
    consistent with previous research indicating that the multiplicity rate is
    high in bright sources discovered in single-dish sub-mm or FIR surveys.
    The ALMA counterparts to our {\it Herschel} targets are located
    significantly closer to each other than ALMA counterparts to sources found
    in the LABOCA ECDFS Submillimeter Survey.  Theoretical models underpredict
    the excess number of sources with small separations seen in our ALMA
    sample.  The high multiplicity rate and low projected separations between
    sources seen in our sample argue in favor of interactions and mergers
    plausibly driving both the prodigious emission from the brightest DSFGs as
    well as the sharp downturn above $S_{880} = 8\,$mJy.

@@

Theoretical expectations based on the redshift distribution and luminosity
function of DSFGs suggested that HerMES and H-ATLAS would be efficient tools
for discovering strongly lensed DSFGs \citep[e.g.,][]{1996MNRAS.283.1340B,
2007MNRAS.377.1557N}.  Submillimeter Array \citep[SMA;][]{Ho:2004lr} imaging at
870$\,\mu$m with sub-arcsecond resolution has confirmed this, with $\geq 85\%$
of the brightest sources found by {\it Herschel} ($S_{500} > 100\,$mJy) being
gravitationally lensed by an intervening galaxy or group of galaxies along the
line of sight \citep{Negrello:2010fk, Conley:2011lr, Riechers:2011uq,
Bussmann:2012lr, Wardlow:2013lr, Bussmann:2013lr}.  Sources discovered in SPT
surveys have also been shown to have a high probability of being strongly
lensed \citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
significantly over-predict the median magnification factor experienced by a
{\it Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
indicate herald new insights in our understanding of the bright end of the
intrinsic DSFG luminosity function or in the nature of the deflectors.

We here present Atacama Large Millimeter/submillimeter Array (ALMA) Cycle~0
imaging at 870$\,\mu$m of a sample of 29 HerMES DSFGs.
%Our targets were selected to be significantly fainter than those reported in
%\citet{Bussmann:2013lr}, so they include a larger number of unlensed or weakly
%lensed ($\mu_{870} < 2$) sources.  
Three aspects of our dataset make it uniquely suited to improving our
understanding of the bright end of the intrinsic DSFG luminosity function.
First, the sample occupies a distinct regime in flux density between the
brightest {\it Herschel} DSFGs (almost all of which are lensed) and much
fainter DSFGs found in ground-based surveys \citep[most of which are expected
to be unlensed; e.g.,][]{Hodge:2013qy}.  Second, the ALMA images are extremely
sensitive ($\sigma \approx 0.2\,$mJy per beam) and all 29 HerMES DSFGs are detected
\citep[which was not the case in previous similar studies with shallower imaging;
e.g.,][]{Smolcic:2012zl, Barger:2012yg, Hodge:2013qy}.  Third, the typical
angular resolutions are $0\farcs45$ and nearly all sources detected by ALMA are
spatially resolved.

@@

In Section~\ref{sec:obs}, we characterize our sample and present our ALMA and
Gemini-South imaging.  Section~\ref{sec:modelfits} presents our model fitting
methodology and model fits for all ALMA sources (lensed and unlensed) using {\sc
uvmcmcfit}, a publicly available
\footnote{\url https://github.com/sbussmann/uvmcmcfit} modified version of the
visibility plane lens modeling software used in \citet{Bussmann:2012lr,
Bussmann:2013lr}.  Results on the effect of lensing for the observed properties
of the {\it Herschel} DSFGs in our sample, as well as the multiplicity rate and
typical angular separation between sources after delensing the ALMA sources,
appear in Section~\ref{sec:results}.  We scrutinize statistical predictions for
$\mu_{870}$ as a function of $S_{870}$ and discuss implications for the bright
end of the DSFG luminosity function in Section~\ref{sec:discuss}.  Finally, we
present our conclusions in Section~\ref{sec:conclusions}.

@@

Figure~\ref{fig:sample} shows that the {\it Herschel}-ALMA sample is set
clearly apart from the very bright {\it Herschel} DSFGs that are selected to
have $S_{500} > 100 \, $mJy and have been shown to be almost entirely lensed
DSFGs \citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast,
the sample in this paper is expected to include a mix of lensed and unlensed
DSFGs.  On the other hand, the HerMES survey area is 200 times larger than that
of the Large Apex Bolometer Camera Extended Chandra Deep Field Survey
\citep[LESS][]{Weis:2009ly}.  This explains why the median $S_{500}$ in our
sample is $\sim4$ times brighter than the median $S_{500}$ in the sample of
ALMA-detected sources in LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it
Herschel}-ALMA sample opens a new window of discovery space on the bright end
of the DSFG luminosity function.

@@

Figure~\ref{fig:delens} shows the observed (i.e., apparent) and intrinsic
(i.e., de-lensed) distributions of $S_{870}$, $r_{\rm s}$, angular separation,
and $q_{\rm s}$.  Here, angular separation is the angular distance between an
ALMA source and the centroid of all the ALMA sources for a given {\it Herschel}
DSFG.  Lensing has the strongest effect on $S_{870}$: the median flux density
in the {\it Herschel}-ALMA sample drops by a factor of 1.6 when lensing is
taken into account. A two-sided Kolmogorov-Smirnov (KS) test yields a $p$-value
of 0.044, suggesting the apparent and intrinsic flux density distributions are
inconsistent with being drawn from the same parent population.  Even if
strongly lensed sources are removed from the sample, the median intrinsic flux
density is 1.3 times lower than the median apparent flux density.  Removing the
unlensed sources from consideration pushes this factor back to 1.6.  At these
levels, failing to correct for amplification due to gravitational lensing will
be a significant source of error, since the absolute calibration uncertainty is
typically of order 5-10\%.  When discussing the intrinsic properties of bright
sources \citep[including their luminosity functions, e.g.][]{Wyithe:2011rm}
discovered in wide-field FIR or mm surveys, it is critical to consider the
effects of lensing.

@@

An excess of sources with small separations from each other could be an
indication of interacting or merging systems.  However, it is also possible
that the sources are merely unrelated galaxies that appear blended due to
projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
to answer this question definitively, but is not currently available.  Instead,
to investigate these possibilities further, we make use of mock catalogs of
DSFGs that are based on numerical simulations and presented by \citet{HB13} and
\citet{Cowley:2015lr}.

@@

To explore this possibility, we investigate mock catalogs based on the
methodology presented in \citet{Cowley:2015lr}.  Here, we give a brief summary
and refer the interested reader to \citet{Cowley:2015lr} for full details. An
updated version of the {\sc galform} \citep[e.g.][Lacey et al. in
preparation]{Cole:2000fk} semi-analytic galaxy formation model is used to
populate halo merger trees \citep[e.g.][]{Parkinson:2008qy, Jiang:2014lr}
derived from a Millennium style $N$-body dark matter only simulation
\citep{Springel:2005lr, Guo:2013lr} with WMAP7 cosmology
\citep{Komatsu:2011fk}.  Submm flux is calculated using a model based on the
radiative transfer.  Dust is assumed to exist in two components,  dense
molecular clouds and a diffuse ISM.  Energy absorbed from starlight by each
dust component is calculated self-consistently.  The dust is then assumed to
emit radiation as a modified blackbody, assuming thermal equilibrium.

Three randomly orientated 20 deg$^2$ lightcone catalogues are generated using
the method described in \citet{Merson:2013lr}.  We choose as the lower flux
limit for inclusion of simulated galaxies into our lightcone catalogue
$S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90 per
cent of the extragalactic background light (EBL) as predicted by our model (122
Jy~deg$^{-2}$). This is in excellent agreement with observations from the
\emph{COBE} satellite \citep[e.g.,][]{Puget:1996lr}. This ensures we have a
realistic 500 $\mu$m  background in our mock images.

Mock imaging is created by binning the lightcone galaxies onto a pixelated grid
which is then convolved with a 36$\arcsec$ FWHM Gaussian (corresponding to the
\emph{Herschel} SPIRE beam at 500$\,\mu$m).  The image is then constrained to
have a zero mean by the subtraction of a uniform background.  No instrumental
noise is added, nor are any further filtering procedures applied to the mock
image.  This procedure is repeated at 350$\,\mu$m and 250$\,\mu$m in order to
provide simulated \emph{Herschel} photometry, adjusting the FWHM of the
Gaussian PSF appropriately and changing the lower limit of inclusion into our
lightcone to ensure 90 per cent of the predicted EBL is recovered at each
wavelength.

Source positions are selected as maxima in the mock 250$\,\mu$m image, with the
position and flux of the source being determined by the maximal pixel.  To
simulate `deblended' \emph{Herschel} photometry we record the value of the
pixel located at the position of the 250$\,\mu$m maxima in the 350$\,\mu$m and
500$\,\mu$m images. We select all \emph{Herschel} sources satisfying
$S_{500\,\mu\rm{m}}>50\,$mJy and $z > 1$ to identify galaxies from our
lightcone catalogs within a 9$\arcsec$ radius of the source position, modelling
the ALMA primary beam profile as a Gaussian with an 18$\arcsec$ FWHM and a
maximum sensitivity of 1$\,$mJy.

@@

%There is some evidence that the intrinsic luminosity function of DSFGs has a
%very steep dropoff at around 8-10$\,$mJy \citep[e.g.,][]{Simpson:2014lr}.  
The distribution of magnification factors for sources found in wide-field
surveys with the brightest apparent flux densities are highly sensitive to the
shape of the intrinsic luminosity function at the bright end.  In this section,
we combine our ALMA and SMA measurements of magnification factors to investigate
this as it pertains to DSFGs.

@@

The key components of the model are the mass density profile of the lenses,
$\rho_{\rm lens}\,(r)$, the number density of lenses as a function of mass and
redshift, $n_{\rm lens}\,(M, \, z),$ the redshift distribution of the sources,
$dN_{\rm source}/dz$, and the intrinsic luminosity function of the sources,
$dn_{\rm source}/dS_{870}^\prime$.  The latter component is the least certain
and also has the strongest impact on the predicted apparent luminosity
function.  For these reasons, we fix all components of the model except the
shape of the intrinsic luminosity function.  Our goal is to take luminosity
functions that can successfully fit observed faint DSFG number counts
\citep{Karim:2013lr} and test whether they lead to predicted magnification
factors consistent with our ALMA and SMA observations.

@@

We explore two intrinsic luminosity functions that are intended to bracket the
plausible range of values for DSFGs based on two interferometric surveys.  One
is the luminosity function measured in ALESS \citep{Karim:2013lr}, and the
other is from interferometric follow-up of the first AzTEC survey in COSMOS
\citep{Scott:2008qy} using the SMA \citep{Younger:2007fk, Younger:2009lr} and
PdBI \citep{Miettinen:2015lr}.  These interferometric observations have shown
that all of the sources in their surveys are either unlensed or lensed by
magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
functions represent a plausible range of intrinsic luminosity functions for
DSFGs.  These luminosity functions are shown in the left panel of
Figure~\ref{fig:lensstats}.  Interferometric follow-up data in COSMOS
\citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are published, but
unknown completeness corrections in the single-dish surveys on which these
follow-up datasets are based precludes their use here.

@@

Table~\ref{tab:models} provides values for the parameters of the broken
power-law for the ALESS and COSMOS luminosity functions.  The data and
corresponding luminosity functions are shown in the left panel of
Figure~\ref{fig:lensstats}.

>>>>

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~C.~Hayward\altaffilmark{4,5},
W.~I.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{6},
J.~Wardlow\altaffilmark{24}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Superieure, CNRS, 24 rue Lhomond, 75005 Paris, France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  The
    ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down
    to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
    Optical or near-infrared imaging indicates that 36 of the ALMA sources
    experience a significant flux boost from gravitational lensing ($\mu >
    1.1$), but only 6 are strongly lensed and show multiple images.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov chain Monte Carlo visibility plane analysis tool to
    analyze the source properties.  Combined with our previous work on brighter
    {\it Herschel} sources, the lens models presented here tentatively favor
    intrinsic number counts for DSFGs with a break near 8$\,$mJy at
    880$\,\mu$m and a steep fall off at higher flux densities.  Nearly 70\% of
    the {\it Herschel} sources break down into multiple ALMA counterparts,
    consistent with previous research indicating that the multiplicity rate is
    high in bright sources discovered in single-dish sub-mm or FIR surveys.
    The ALMA counterparts to our {\it Herschel} targets are located
    significantly closer to each other than ALMA counterparts to sources found
    in the LABOCA ECDFS Submillimeter Survey.  Theoretical models underpredict
    the excess number of sources with small separations seen in our ALMA
    sample.  The high multiplicity rate and low projected separations between
    sources seen in our sample argue in favor of interactions and mergers
    plausibly driving both the prodigious emission from the brightest DSFGs as
    well as the sharp downturn above $S_{880} = 8\,$mJy.

@@

Theoretical expectations based on the redshift distribution and luminosity
function of DSFGs suggested that HerMES and H-ATLAS would be efficient tools
for discovering strongly lensed DSFGs \citep[e.g.,][]{1996MNRAS.283.1340B,
2007MNRAS.377.1557N}.  Submillimeter Array \citep[SMA;][]{Ho:2004lr} imaging at
870$\,\mu$m with sub-arcsecond resolution has confirmed this, with $\geq 85\%$
of the brightest sources found by {\it Herschel} ($S_{500} > 100\,$mJy) being
gravitationally lensed by an intervening galaxy or group of galaxies along the
line of sight \citep{Negrello:2010fk, Conley:2011lr, Riechers:2011uq,
Bussmann:2012lr, Wardlow:2013lr, Bussmann:2013lr}.  Sources discovered in SPT
surveys have also been shown to have a high probability of being strongly
lensed \citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
significantly over-predict the median magnification factor experienced by a
{\it Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
herald new insights in our understanding of the bright end of the
intrinsic DSFG number counts or in the nature of the deflectors.

We here present Atacama Large Millimeter/submillimeter Array (ALMA) Cycle~0
imaging at 870$\,\mu$m of a sample of 29 HerMES DSFGs.
%Our targets were selected to be significantly fainter than those reported in
%\citet{Bussmann:2013lr}, so they include a larger number of unlensed or weakly
%lensed ($\mu_{870} < 2$) sources.  
Three aspects of our dataset make it uniquely suited to improving our
understanding of the bright end of the intrinsic DSFG number counts.
First, the sample occupies a distinct regime in flux density between the
brightest {\it Herschel} DSFGs (almost all of which are lensed) and much
fainter DSFGs found in ground-based surveys \citep[most of which are expected
to be unlensed; e.g.,][]{Hodge:2013qy}.  Second, the ALMA images are extremely
sensitive ($\sigma \approx 0.2\,$mJy per beam) and all 29 HerMES DSFGs are detected
\citep[which was not the case in previous similar studies with shallower imaging;
e.g.,][]{Smolcic:2012zl, Barger:2012yg, Hodge:2013qy}.  Third, the typical
angular resolutions are $0\farcs45$ and nearly all sources detected by ALMA are
spatially resolved.

@@

In Section~\ref{sec:obs}, we characterize our sample and present our ALMA and
Gemini-South imaging.  Section~\ref{sec:modelfits} presents our model fitting
methodology and model fits for all ALMA sources (lensed and unlensed) using {\sc
uvmcmcfit}, a publicly available
\footnote{\url https://github.com/sbussmann/uvmcmcfit} modified version of the
visibility plane lens modeling software used in \citet{Bussmann:2012lr,
Bussmann:2013lr}.  Results on the effect of lensing for the observed properties
of the {\it Herschel} DSFGs in our sample, as well as the multiplicity rate and
typical angular separation between sources after delensing the ALMA sources,
appear in Section~\ref{sec:results}.  We scrutinize statistical predictions for
$\mu_{870}$ as a function of $S_{870}$ and discuss implications for the bright
end of the DSFG number counts in Section~\ref{sec:discuss}.  Finally, we
present our conclusions in Section~\ref{sec:conclusions}.

@@

Figure~\ref{fig:sample} shows that the {\it Herschel}-ALMA sample is set
clearly apart from the very bright {\it Herschel} DSFGs that are selected to
have $S_{500} > 100 \, $mJy and have been shown to be almost entirely lensed
DSFGs \citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast,
the sample in this paper is expected to include a mix of lensed and unlensed
DSFGs.  On the other hand, the HerMES survey area is 200 times larger than that
of the Large Apex Bolometer Camera Extended Chandra Deep Field Survey
\citep[LESS][]{Weis:2009ly}.  This explains why the median $S_{500}$ in our
sample is $\sim4$ times brighter than the median $S_{500}$ in the sample of
ALMA-detected sources in LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it
Herschel}-ALMA sample opens a new window of discovery space on the bright end
of the DSFG number counts.

@@

Figure~\ref{fig:delens} shows the observed (i.e., apparent) and intrinsic
(i.e., de-lensed) distributions of $S_{870}$, $r_{\rm s}$, angular separation,
and $q_{\rm s}$.  Here, angular separation is the angular distance between an
ALMA source and the centroid of all the ALMA sources for a given {\it Herschel}
DSFG.  Lensing has the strongest effect on $S_{870}$: the median flux density
in the {\it Herschel}-ALMA sample drops by a factor of 1.6 when lensing is
taken into account. A two-sided Kolmogorov-Smirnov (KS) test yields a $p$-value
of 0.044, suggesting the apparent and intrinsic flux density distributions are
inconsistent with being drawn from the same parent population.  Even if
strongly lensed sources are removed from the sample, the median intrinsic flux
density is 1.3 times lower than the median apparent flux density.  Removing the
unlensed sources from consideration pushes this factor back to 1.6.  At these
levels, failing to correct for amplification due to gravitational lensing will
be a significant source of error, since the absolute calibration uncertainty is
typically of order 5-10\%.  When discussing the intrinsic properties of bright
sources \citep[including their number counts, e.g.][]{Wyithe:2011rm}
discovered in wide-field FIR or mm surveys, it is critical to consider the
effects of lensing.

@@

An excess of sources with small separations from each other could be an
indication of interacting or merging systems.  However, it is also possible
that the sources are merely unrelated galaxies that appear blended due to
projection effects \citep{HB13, Cowley:2015lr, Munoz-Arancibia:2015qy}.
Spatially resolved spectroscopy is necessary to answer this question
definitively, but is not currently available.  Instead, to investigate these
possibilities further, we make use of mock catalogs of DSFGs that are based on
numerical simulations and presented by \citet{HB13} and \citet{Cowley:2015lr}.

@@

To explore this possibility, we investigate mock catalogs based on the
methodology presented in \citet{Cowley:2015lr}.  Here, we give a brief summary
and refer the interested reader to \citet{Cowley:2015lr} for full details. A
new version of the {\sc galform} \citep[e.g.][Lacey et al. in
preparation]{Cole:2000fk} semi-analytic model of hierarchical galaxy formation
is used to populate halo merger trees \citep[e.g.][]{Parkinson:2008qy,
Jiang:2014lr} derived from a Millennium style $N$-body dark matter only
simulation \citep{Springel:2005lr, Guo:2013lr} with WMAP7 cosmology
\citep{Komatsu:2011fk}.  A sub-mm flux for each galaxy is calculated using a
self-consistent model based on radiative transfer and energy balance arguments.
Dust is assumed to exist in two components,  dense molecular clouds and a
diffuse ISM.  Energy absorbed from stellar radiation by each dust component is
calculated by solving the equations of radiative transfer in an assumed dust
geometry.  The dust is then assumed to emit radiation as a modified blackbody.

Three randomly orientated 20 deg$^2$ lightcone catalogues are generated using
the method described in \citet{Merson:2013lr}.  We choose as the lower flux
limit for inclusion of simulated galaxies into our lightcone catalogue
$S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90\% of
the extragalactic background light (EBL) as predicted by the model (122
Jy~deg$^{-2}$). This is in excellent agreement with observations from the
\emph{COBE} satellite \citep[e.g.,][]{Puget:1996lr}, and thus ensures a
realistic 500 $\mu$m  background in the mock images.

Mock imaging is created by binning the lightcone galaxies onto a pixelated grid
which is then convolved with a 36$\arcsec$ FWHM Gaussian (corresponding to the
\emph{Herschel}/SPIRE beam at 500$\,\mu$m).  The image is then constrained to
have a zero mean by the subtraction of a uniform background.  No instrumental
noise is added, nor are any further filtering procedures applied to the mock
image.  For the purposes of source identification, this procedure is repeated
at 250$\,\mu$m.  For this, we adjust the FWHM of the Gaussian PSF to
18$\arcsec$ and change the lower flux limit of inclusion into our lightcone to
ensure 90\% of the predicted EBL is recovered at this wavelength.

Source positions are selected as maxima in the mock 250$\,\mu$m image, with the
position of the source being recorded as the center the maximal pixel for
simplicity.  To mimic `deblended' \emph{Herschel} photometry we record the
value of the pixel located at the position of the 250$\,\mu$m maxima in the
500$\,\mu$m images. We select all \emph{Herschel} sources satisfying
$S_{500\,\mu\rm{m}}>50\,$mJy and $z > 1$ to identify galaxies from our
lightcone catalogs within a 9$\arcsec$ radius of the source position, modelling
the ALMA primary beam profile as a Gaussian with an 18$\arcsec$ FWHM and a
maximum sensitivity of 1$\,$mJy.

@@

%There is some evidence that the intrinsic luminosity function of DSFGs has a
%very steep dropoff at around 8-10$\,$mJy \citep[e.g.,][]{Simpson:2014lr}.  
The distribution of magnification factors for sources found in wide-field
surveys with the brightest apparent flux densities are highly sensitive to the
shape of the intrinsic number counts at the bright end.  In this section,
we combine our ALMA and SMA measurements of magnification factors to investigate
this as it pertains to DSFGs.

@@

The key components of the model are the mass density profile of the lenses,
$\rho_{\rm lens}\,(r)$, the number density of lenses as a function of mass and
redshift, $n_{\rm lens}\,(M, \, z),$ the redshift distribution of the sources,
$dN_{\rm source}/dz$, and the intrinsic number counts of the sources,
$dn_{\rm source}/dS_{870}^\prime$.  The latter component is the least certain
and also has the strongest impact on the predicted apparent luminosity
function.  For these reasons, we fix all components of the model except the
shape of the intrinsic number counts.  Our goal is to take luminosity
functions that can successfully fit observed faint DSFG number counts
\citep{Karim:2013lr} and test whether they lead to predicted magnification
factors consistent with our ALMA and SMA observations.

@@

We explore two intrinsic number counts that are intended to bracket the
plausible range of values for DSFGs based on two interferometric surveys.  One
is the number counts measured in ALESS \citep{Karim:2013lr}, and the
other is from interferometric follow-up of the first AzTEC survey in COSMOS
\citep{Scott:2008qy} using the SMA \citep{Younger:2007fk, Younger:2009lr} and
PdBI \citep{Miettinen:2015lr}.  These interferometric observations have shown
that all of the sources in their surveys are either unlensed or lensed by
magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
functions represent a plausible range of intrinsic number counts for
DSFGs.  These number counts are shown in the left panel of
Figure~\ref{fig:lensstats}.  Interferometric follow-up data in COSMOS
\citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are published, but
unknown completeness corrections in the single-dish surveys on which these
follow-up datasets are based precludes their use here.

@@

Table~\ref{tab:models} provides values for the parameters of the broken
power-law for the ALESS and COSMOS number counts.  The data and
corresponding number counts are shown in the left panel of
Figure~\ref{fig:lensstats}.
